Supernova Host Galaxies in the Dark Energy Survey: \\ II. Rapidly Evolving Transients

### 2020-02-25 RET_Hosts.tex

\section{Discussion \label{sec:disc}}

\subsection{Selection Biases \label{subsec:disc_bias}}
The properties presented in Section \ref{sec:analysis} are derived from a subset of the total sample of RETs. Of 106 objects, under half (49/106) have secure host galaxy redshifts. Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and six were obtained by programmes for which we do not have access to the spectra. Of the remaining 42, it was possible to derive a metallicity for 37 host galaxies. The observed metallicity distribution could have arisen if the galaxies without redshifts (and metallicities) are systematically higher in metallicity than those for which measurements were possible. This scenario is unlikely. For low SNR objects, redshifts are typically obtained from only two of the strongest lines (e.g. \halpha, \hbeta, \OIII, and \OII), whose absolute luminosity is not strongly dependent on metallicity. It is likely that the redshifts were not obtained because of low SNR, caused by the galaxies being smaller and at higher redshift. We do not envisage a plausible scenario where those galaxies are systematically higher in metallicity.

@@

\subsection{Correlations with lightcurve properties}

>>>>

\section{Discussion \label{sec:disc}}
\begin{figure}
\includegraphics[width=0.5\textwidth]{figs/RET_vs_host.png}
\caption{RET lightcurve properties as a function of host galaxy measurements.
\label{fig:ret_v_host}}
\end{figure}
\subsection{Selection Biases \label{subsec:disc_bias}}
The properties presented in Section \ref{sec:analysis} are derived from a subset of the total sample of RETs. Of 106 objects, under half (49/106) have secure host galaxy redshifts. Three of these were obtained from transient spectra, for which we are unable to disentangle the host and transient contributions, and six were obtained by programmes for which we do not have access to the spectra. Of the remaining 42, it was possible to derive a metallicity for 37 host galaxies. The observed metallicity distribution could have arisen if the galaxies without redshifts (and metallicities) are systematically higher in metallicity than those for which measurements were possible. This scenario is unlikely. For low SNR objects, redshifts are typically obtained from only two of the strongest lines (e.g. \halpha, \hbeta, \OIII, and \OII), whose absolute luminosity is not strongly dependent on metallicity. It is likely that the redshifts were not obtained because of low SNR, caused by the galaxies being smaller and at higher redshift. We do not envisage a plausible scenario where those galaxies are systematically higher in metallicity.

@@

\subsection{Correlations between lightcurve and host galaxy properties}
Many classes of transients show trends between properties intrinsic to the objects themselves and their host galaxies. For example, SNe Ia lightcurves appear to be broader in less massive galaxies with higher sSFR \citep{Sullivan2006,Neill2009,Howell2009,Sullivan2010,Roman2018,Kelsey2020}, while SLSNe that have been fit with a magnetar model show a tentative relationship between the magnetar spin period and host galaxy metallicity \citep{Chen2016a}. In Fig. \ref{fig:ret_v_host} we show the RET peak magnitude (upper pannels) and decline rate parameterised as $t_{\mathrm{half}}$, the time taken for the LC to decline to half the peak brightness (lower panels) and how they correspond to host galaxy stellar mass (left-hand panels) and sSFR (right-hand panels).
